Reanalysis Step 4: Outcome Analysis with Three-Way Interaction

### 2025-08-20 reanalysis-4-outcome_analysis.qmd
fix vcov

# Get pooled variance-covariance matrix for later calculations
pooled_vcov <- vcov(pooled_model)

@@

>>>>

@@

# Construct pooled variance-covariance matrix from the pooled variances
# mice::pool returns a mipo object which stores variances in pooled$t
# We need to create a diagonal matrix since pool() doesn't provide covariances
pooled_variances <- pooled_model$pooled$t
pooled_vcov <- diag(pooled_variances)
rownames(pooled_vcov) <- pooled_model$pooled$term
colnames(pooled_vcov) <- pooled_model$pooled$term
